Network Slicing and Resource Allocation in an Open RAN System \vspace{-.1cm}

### 2020-12-22 Latex/journal_v1/V2/pr.tex
add file

In this section, first, we  present the system model. Then, we obtain achievable data rates and delays for the downlink (DL) of the ORAN system. Afterward, we discuss about assignment of physical data center resources.
Finally, the main problem is expressed.
\subsection{System Model}
Suppose we have two service types includes eMBB and URLLC. Assume we have $V_1$ and $V_2$ different applications for the first and second service type, respectively ($V = V_1 + V_2$).
Assume we have $S$ preallocated slices serving $V$ services; There are $S_1$ slices for the first service type (eMBB) and $S_2$ slices for the second service type (URLLC) ($S = S_1 + S_2$).
Each Service $v_j\in \{1,2,...,V_j \} $ consists of $U_{v_j}$ request from the 
single-antenna UEs which require certain QoS to be able to use the requested program($j \in \{1,2\}$ indicate service type).
There are different application request which fall into one of these service categories. Each application request requires specific QoS. Based on the request for the application and QoS, UE may be admitted and allocated to slice.
Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2\}$ consists of $K_{s_j}$, $j \in \{1,2\}$ preallocated virtual resource blocks that are mapped to Physical Resource Blocks (PRBs), $M_s^{d}$ VNFs for the processing of O-DU,  $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF.

@@

In addition, there are $R$ multi-antenna RU that are shared between slices. Each RU $r \in \{1,2,...,R \}$
has $J$ antenna for transmitting and receiving data. Moreover, all RUs, have access to PRBs.
\subsection{The Achievable Rate}
The SNR of $i^{th}$ UE in $v^{th}$ service experienced at slice $s$ on PRB $k$ which is obtained from
 $\rho_{u(v,i)}^{k,s}$ is the SNR 
\begin{equation}\label{eq2}
\rho_{u(v,i)}^{k,s} =  \sum_{r=1}^{R}\frac{|p_{r,u(v,i)}^{k,s}{\bold{h}_{r,u(v,i)}^{H \: k,s}} \bold{w}_{r,u(v,i)}^{k,s} g_{u(v,i)}^r|^2}{BN_0 + I_{r,u(v,i)}^{k,s}},
\end{equation} 
where $p_{r,u(v,i)}^{k,s}$ represents the transmission power from o-RU $r$ to $i^{th}$ UE in $v^{th}$ service, served at slice $s$ on PRB $k$. 
${\bold{h}_{r,u(v,i)}^{k,s}} \in \mathbb{C}^{J}$ is the vector of channel gain of a wireless link from 
$r^{th}$ RU to the $i^{th}$ UE in $v^{th}$ service. In addition, $\bold{w}_{r,u(v,i)}^{k,s} \in \mathbb{C}^{J}$ depicts the  transmit beamforming vector from $r^{th}$ RU to the $i^{th}$ UE in $v^{th}$ service that is the zero forcing beamforming vector to minimize the interference which is indicated as below
\begin{equation}
\bold{w}_{r,u(v,i)}^{k,s} = {\bold{h}_{r,u(v,i)}^{k,s}}({\bold{h}_{r,u(v,i)}^{H \: k,s1}} {\bold{h}_{r,u(v,i)}^{k,s}})^{-1}
\end{equation}
Moreover, $g_{u(v,i)}^r \in \{0,1\}$ is a binary variable that illustrates whether RU $r$ is mapped to the $i^{th}$ UE in $v_{1}^{th}$ service or not. 
Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{r,u(v,i)}^{k,s1}$ is the power of interfering signals represented as follow
\begin{equation}
\begin{split}
I_{r,u(v,i)}^{k,s} &=
 \underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{v}} \gamma_{1}  p_{u(v,i)}^{k,s}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(v,i)}^{H \: k,s}} \bold{w}_{r',u(v,i)}^{k,s1} g_{u(v,i)}^{r'}|^2}_{\text{(intra-service interference)}}\\
&+ \underbrace{\sum_{\substack{y=1 \\ l\neq v}}^{V}\sum_{n=1}^{S}\sum_{l=1}^{{U}_y} \gamma_{2}  p_{u(y,l)}^{k,n}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(v,i)}^{H \: k,s}} \bold{w}_{r',u(y,l)}^{k,n} g_{u(y,l)}^{r'}|^2}_{\text{(inter-service interference)}}\\
\end{split}
\end{equation}
where $\gamma_{1} = e^{k,s}_{r,u(v,i)}e^{k,s}_{r',u(v,l)}a_{u(v,i)}a_{u(v,l)} b_{v, s} $
and $\gamma_{2} = e^{k,s}_{r,u(v,i)}e^{k,n}_{r',u(y,l)}a_{u(v,i)}a_{u(y,l)} b_{v, s} b_{y,n} $.
Where $a_{u(v,i)} \in \{0,1\}$ is a binary variable to depict user admission.
$b_{v, s}$ is a binary variable that illustrates whether slice $s$ is allocated to service $v$ or not. 
$e^{k,s}_{r,u(v,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in service $v$, assigned to $r^{th}$ o-RU using slice $s$ or not.

@@

\subsection{Mean Delay}
In this part, the end to end mean delay for a service is obtained.
Suppose the mean total delay is depicted as $T_{tot}$.
\begin{equation}
\begin{split}
T_{tot} &=  T_{process} + T_{transmission} + T_{propagation}\\
T_{process} &=  T_{RU} + T_{DU} + T_{CU} + T_{UPF}\\
T_{transmission} &= T_{front} + T_{mid} + T_{back} + T_{trans2net} \\
T_{propagation} &= T_{front} + T_{mid} + T_{back} + T_{trans2net} \\
\end{split}
\end{equation}
%T_{tot} = T_{RU} + T_{front} + T_{DU} + T_{mid} + T_{CU} + T_{back} + T_{core} + T_{trans2net}
Total delay is sum of processing delay, transmission delay and propagation delay. 
The propagation delay is the time takes for a signal to reach to its destination. So it has a constant value based on the length of fiber link ($T = L/c$, where $L$ is the length of link and c is the speed of signal).
Here we assume the value of propagation delay is negligible compared to the rest.
\subsubsection{Processing Delay}
Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda_{u(v,i)}$ for the $i^{th}$ UE of the $v^{th}$ service.
Therefore, the mean arrival data rate of the $v^{th}$ service in the UPF layer is $\alpha_{v}^1 = \sum_{u=1}^{U_v}a_{u(v,i)}\lambda_{u(v,i)}$, where $a_{u(v,i)}$ is a binary variable which indicates whether the $i^{th}$ UE requested $v^{th}$ service is admitted or not.

@@

where, $R_{{tot}_v} = \sum_{u=1}^{U_v}a_{u(v,i)}R_{u(v,i)}$ is the total achievable rate of each service.

@@

P_r =  \sum_{v=1}^{V} \sum_{i=1}^{U_v} \sum_{s=1}^{S} \sum_{k=1}^{K_s}p_{r,u(v,i)}^{k,s}a_{u(v,i)} b_{v, s} e^{k,s}_{r,u(v,i)}g_{u(v,i)}^r.

@@

&p_{r,u(v,i)}^{k,s}  \geq 0  \quad \forall v,\forall i,\forall r,\forall s, \forall k,\label{c12} \\

@@

&a_{u(v,i)} \leq a_{u(v,i)}\sum_{r}g^r_{u(v,i)} \leq 1 \quad \forall v,\forall i  \\
& \sum_{s=1}^{S}\sum_{v=1}^{V}\sum_{i=1}^{U_v}a_{u(v,i)}g^r_{u(v,i)}e^{k,s}_{r,u(v,i)} \leq 1 \quad \forall r, \label{c21} \\

>>>>

In this section, first, we  present the system model. Then, we obtain achievable data rates and delays for the downlink (DL) of the ORAN system. Afterward, we discuss about assignment of physical data center resources.
Finally, the main problem is expressed.
\subsection{System Model}
Suppose we have two service types includes eMBB and URLLC. Assume we have $S_1$ and $S_2$ different applications for the first and second service type, respectively ($S = S_1 + S_2$).
Assume we have $S$ preallocated slices serving these $S$ services; There are $S_1$ slices for the first service type (eMBB) and $S_2$ slices for the second service type (URLLC).
Each Service $s_j\in \{1,2,...,S_j \} $ consists of $U_{s_j}$ request from the 
single-antenna UEs which require certain QoS to be able to use the requested program($j \in \{1,2\}$ indicate service type).
There are different application request which fall into one of these service categories. Each application request requires specific QoS. Based on the request for the application and QoS, UE may be admitted and allocated to the resources.
Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2\}$ consists of $K_{s_j}$, $j \in \{1,2\}$ preallocated virtual resource blocks that are mapped to Physical Resource Blocks (PRBs), $M_s^{d}$ VNFs for the processing of O-DU,  $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF.

@@

In addition, there are $R$ multi-antenna RU that are shared between slices. Each RU $r \in \{1,2,...,R \}$
has $J$ antenna for transmitting and receiving data. Moreover, all RUs, have access to PRBs.
\subsection{The Achievable Rate}
The SNR of $i^{th}$ UE in $v^{th}$ service experienced at slice $s$ on PRB $k$ which is obtained from
 $\rho_{u_i}^{k,s}$ is the SNR 
\begin{equation}\label{eq2}
\rho_{u_i}^{k,s} =  \sum_{r=1}^{R}\frac{|p_{r,u_i}^{k,s}{\bold{h}_{r,u_i}^{H \: k,s}} \bold{w}_{r,u_i}^{k,s} g_{u_i}^r|^2}{BN_0 + I_{r,u_i}^{k,s}},
\end{equation} 
where $p_{r,u_i}^{k,s}$ represents the transmission power from o-RU $r$ to $i^{th}$ UE in $v^{th}$ service, served at slice $s$ on PRB $k$. 
${\bold{h}_{r,u_i}^{k,s}} \in \mathbb{C}^{J}$ is the vector of channel gain of a wireless link from 
$r^{th}$ RU to the $i^{th}$ UE in $v^{th}$ service. In addition, $\bold{w}_{r,u_i}^{k,s} \in \mathbb{C}^{J}$ depicts the  transmit beamforming vector from $r^{th}$ RU to the $i^{th}$ UE in $v^{th}$ service that is the zero forcing beamforming vector to minimize the interference which is indicated as below
\begin{equation}
\bold{w}_{r,u_i}^{k,s} = {\bold{h}_{r,u_i}^{k,s}}({\bold{h}_{r,u_i}^{H \: k,s1}} {\bold{h}_{r,u_i}^{k,s}})^{-1}
\end{equation}
Moreover, $g_{u_i}^r \in \{0,1\}$ is a binary variable that illustrates whether RU $r$ is mapped to the $i^{th}$ UE in $v_{1}^{th}$ service or not. 
Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{r,u_i}^{k,s1}$ is the power of interfering signals represented as follow
\begin{equation}
\begin{split}
I_{r,u_i}^{k,s} &=
 \underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{v}} \gamma_{1}  p_{u_i}^{k,s}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u_i}^{H \: k,s}} \bold{w}_{r',u_i}^{k,s1} g_{u_i}^{r'}|^2}_{\text{(intra-service interference)}}\\
&+ \underbrace{\sum_{\substack{y=1 \\ l\neq v}}^{V}\sum_{n=1}^{S}\sum_{l=1}^{{U}_y} \gamma_{2}  p_{u(y,l)}^{k,n}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u_i}^{H \: k,s}} \bold{w}_{r',u(y,l)}^{k,n} g_{u(y,l)}^{r'}|^2}_{\text{(inter-service interference)}}\\
\end{split}
\end{equation}
where $\gamma_{1} = e^{k,s}_{r,u_i}e^{k,s}_{r',u(v,l)}a_{u_i}a_{u(v,l)} b_{v, s} $
and $\gamma_{2} = e^{k,s}_{r,u_i}e^{k,n}_{r',u(y,l)}a_{u_i}a_{u(y,l)} b_{v, s} b_{y,n} $.
Where $a_{u_i} \in \{0,1\}$ is a binary variable to depict user admission.
$b_{v, s}$ is a binary variable that illustrates whether slice $s$ is allocated to service $v$ or not. 
$e^{k,s}_{r,u_i}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in service $v$, assigned to $r^{th}$ o-RU using slice $s$ or not.

@@

\subsection{Mean Delay}
In this part, the end to end mean delay for a service is obtained.
Suppose the mean total delay is depicted as $T_{tot}$.
\begin{equation}
\begin{split}
T_{tot} &=  T_{process} + T_{transmission} + T_{propagation}\\
T_{process} &=  T_{RU} + T_{DU} + T_{CU} + T_{UPF}\\
T_{transmission} &= T_{front} + T_{mid} + T_{back} + T_{trans2net} \\
T_{propagation} &= T_{front} + T_{mid} + T_{back} + T_{trans2net} \\
\end{split}
\end{equation}
%T_{tot} = T_{RU} + T_{front} + T_{DU} + T_{mid} + T_{CU} + T_{back} + T_{core} + T_{trans2net}
Total delay is sum of processing delay, transmission delay and propagation delay. 
The propagation delay is the time takes for a signal to reach to its destination. So it has a constant value based on the length of fiber link ($T = L/c$, where $L$ is the length of link and c is the speed of signal).
Here we assume the value of propagation delay is negligible compared to the rest.
\subsubsection{Processing Delay}
Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda_{u_i}$ for the $i^{th}$ UE of the $v^{th}$ service.
Therefore, the mean arrival data rate of the $v^{th}$ service in the UPF layer is $\alpha_{v}^1 = \sum_{u=1}^{U_v}a_{u_i}\lambda_{u_i}$, where $a_{u_i}$ is a binary variable which indicates whether the $i^{th}$ UE requested $v^{th}$ service is admitted or not.

@@

where, $R_{{tot}_v} = \sum_{u=1}^{U_v}a_{u_i}R_{u_i}$ is the total achievable rate of each service.

@@

P_r =  \sum_{v=1}^{V} \sum_{i=1}^{U_v} \sum_{s=1}^{S} \sum_{k=1}^{K_s}p_{r,u_i}^{k,s}a_{u_i} b_{v, s} e^{k,s}_{r,u_i}g_{u_i}^r.

@@

&p_{r,u_i}^{k,s}  \geq 0  \quad \forall v,\forall i,\forall r,\forall s, \forall k,\label{c12} \\

@@

&a_{u_i} \leq a_{u_i}\sum_{r}g^r_{u_i} \leq 1 \quad \forall v,\forall i  \\
& \sum_{s=1}^{S}\sum_{v=1}^{V}\sum_{i=1}^{U_v}a_{u_i}g^r_{u_i}e^{k,s}_{r,u_i} \leq 1 \quad \forall r, \label{c21} \\
